---
title: "Data 621 - Homework 3"
author: "Anthony Munoz"
date: "4/5/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: lumen
    highlight: pygments
  pdf_document:
    df_print: kable
    toc: true
    toc_depth: 2
---
```{r message=FALSE, warning=TRUE}
library(caret)
library(dplyr)
library(psych)
library(corrplot)
library(tidyr)
library(ggplot2)
library(VIM)
library(ResourceSelection)
library(pROC)


```

## Data Exploration 

```{r}

train.data <- read.csv('crime-training-data_modified.csv')
head(train.data)

str(train.data)
summary(train.data)
```
```{r}

ggplot(stack(train.data), aes(x = ind, y = values)) + 
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 100)) 

  

```
```{r}


pairs.panels(train.data)

corrplot(cor(train.data))

ggplot(gather(train.data), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free')


```
After observing the correlation plot and variables distribution we can see they are a couple of variables that need to be addressed. we don't have missing values as it shows on the data summary, but we see some high correlation between variables (rad-tax). We also can see some skewed data on some variables.

After the observation,we going to proceed with some data transformations methods and log variables in order to normalize the data for our modeling process.

## Data Preparation

We decided to remove the Rad variable because it's highly correlated with the Tax variable. we proceed to do the log method to the variables(lstat,nox,dis), I tried to also work with the log method to the variable ZN but I realized it transforms some fo the observation to infinity values for which then get the drop when using for modeling. Another solution for zn variable could be to add 1 to the value of zeros.
```{r}
data.new <- train.data
train.data$lstat <- log(train.data$lstat)
train.data$nox <- log(train.data$nox +1)
train.data$dis <- log(train.data$dis)
train.data$zn <- log(train.data$zn + 1)
train.df <- subset( train.data, select = -rad )


ggplot(gather(train.data), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free')


```
After some of the transformation, we can see that some variables seem better with the perspective of the distribution on the Histogram plot.

## Build Models
### Model 1
```{r}
model1 <- glm(target~.,  data = train.df, family = "binomial")

summary(model1)

plot(model1)

hoslem.test(data.new$target, fitted(model1))
```

### Model 2

```{r}
model2  <- glm(target~chas + nox + age+ dis+ tax+ medv + indus,  data =train.df, family = "binomial")
summary(model2)

plot(model2)

hoslem.test(data.new$target, fitted(model2))
```

### Model 3

```{r}

df.tranformed <- predict(preProcess(data.new[,-13], c("BoxCox")), data.new[,-13])

model3  <- glm(data.new$target~.,  data =df.tranformed, family = "binomial")
summary(model3)
#plot(model3)




hoslem.test(data.new$target, fitted(model3))
```

### Model 4

```{r}

df.tranformed <- predict(preProcess(data.new[,-13], c("BoxCox")), data.new[,-13])

model4  <- glm(data.new$target ~ nox +  dis + rad+ ptratio+age+medv,  data =df.tranformed, family = "binomial")
summary(model4)
plot(model4)

hoslem.test(data.new$target, fitted(model4))

```
## Select Model

After working with different model solutions for our data, we going to select model # 4 taking into consideration it has the lowest AIC value of 216. Model number #4 is created using the Boxcox transformation and also selecting the most significant variables.

```{r}
test.data <- as.data.frame(scale(read.csv('crime-evaluation-data_modified.csv')))

df.tranformed$pred<- predict(model4, df.tranformed, interval="response")
df.tranformed$target.pred<- ifelse(df.tranformed$pred >= 0.52, 1, 0)  

confusionMatrix(factor(df.tranformed$target.pred),factor(data.new$target))


roc(data.new$target, df.tranformed$pred, plot=TRUE, asp=NA,
                legacy.axes=TRUE, col="red")



coords(roc.value, "best")







#Testing Data

test.data$pred <- predict(model4, newdata = test.data, interval="response")
test.data$target.pred<- ifelse(test.data$pred >= 0.52, 1, 0)  
test.data

write.csv(test.data,"test_data_pred.csv")

```

## Appendix

