---
title: "Homework_4"
author: "Anthony Munoz"
date: "4/26/2020"
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    highlight: haddock
    theme: yeti
    toc: yes
    toc_depth: 5
    toc_float: yes
---
```{r include=FALSE}

knitr::opts_chunk$set(echo=FALSE)
```



```{r message=FALSE, warning=FALSE}
library(caret)
library(dplyr)
library(psych)
library(corrplot)
library(tidyr)
library(ggplot2)
library(VIM)
library(ResourceSelection)
library(pROC)
library(tidyverse)

```


## Data Exploration 


```{r}
data <- read.csv('insurance_training_data (1).csv')

str(data)

summary(data)
```


```{r}

ggplot(stack(data), aes(x = ind, y = values)) + 
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 100)) 



ggplot(gather(select_if(data,is.numeric)), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free')

```

From the graph, we can see that just the Age variable is normally distributed. TRAVELTIME,YOJ, CAR_AGE seem distributed but they are skewed data, which will require some data transformation to fix them.

## Data Preparation

```{r}


sapply(data, class)

colnames(data)

col <- c("HOME_VAL","OLDCLAIM","INCOME","BLUEBOOK")
data[col] <- sapply(data[col],as.numeric)

data$INCOME <- str_replace_all(data$INCOME, "[\\$,]", "")
data$HOME_VAL <- str_replace_all(data$HOME_VAL, "[\\$,]", "")
data$BLUEBOOK <-  str_replace_all(data$BLUEBOOK, "[\\$,]", "")
data$OLDCLAIM <- str_replace_all(data$OLDCLAIM, "[\\$,]", "")

col <- c("HOME_VAL","OLDCLAIM","INCOME","BLUEBOOK")
data[col] <- sapply(data[col],as.numeric)

Amelia::missmap(data)


sapply(data,function(i)sum(is.na(i)))


data$AGE[is.na(data$AGE)] <- mean(data$AGE, na.rm=T)
data$YOJ[is.na(data$YOJ)] <- mean(data$YOJ, na.rm=T)
data$CAR_AGE[is.na(data$CAR_AGE)] <- mean(data$CAR_AGE, na.rm=T)
data$HOME_VAL[is.na(data$HOME_VAL)]  <- mean(data$HOME_VAL, na.rm=T)
data$OLDCLAIM[is.na(data$OLDCLAIM)] <- mean(data$OLDCLAIM, na.rm=T)
data$INCOME[is.na(data$INCOME)] <- mean(data$INCOME, na.rm=T)


Amelia::missmap(data)

```

We can see some variables are missing some observation. in order to work with them, we decide to impute the data by the mean of those variables.

```{r}

train_data <- data

train_data$MSTATUS <- ifelse(train_data$MSTATUS == "Yes", 1, 0)  

train_data$SEX <- ifelse(train_data$SEX == 'M', 1, 0)  


train_data$PARENT1 <- ifelse(train_data$PARENT1 == "Yes", 1, 0)  

train_data$CAR_USE <- ifelse(train_data$CAR_USE == "Private", 1, 0)  

train_data$RED_CAR <- ifelse(train_data$RED_CAR == "yes", 1, 0)  
train_data$REVOKED <- ifelse(train_data$REVOKED == "Yes", 1, 0)  

train_data$EDUCATION <- ifelse(train_data$EDUCATION == "<High School", 0, 1)  
train_data$URBANICITY <- ifelse(train_data$URBANICITY == "Highly Urban/ Urban", 1, 0)  





```


## Model
### Multiple Linear Regression Model

```{r}
## model 1
dat <- train_data[,-1]

model1 <- lm(TARGET_AMT ~., data = dat)

summary(model1)

plot(model1)


## Model 2
model2 <- lm(TARGET_AMT ~BLUEBOOK + REVOKED + MVR_PTS, data = dat)

summary(model2)

plot(model2)

## Model 3

model3 <- lm(TARGET_AMT ~ log10(BLUEBOOK)+ REVOKED + MVR_PTS, data = dat)

summary(model3)
plot(model3)

```

### Logistic Regression Model

```{r}
## Model 4

model4 <- glm(TARGET_FLAG ~ HOME_VAL + PARENT1 + MSTATUS + SEX + EDUCATION + CAR_USE + RED_CAR +REVOKED,  data = dat, family = "binomial")

summary(model4)

plot(model4)

## Model 5

model5 <- glm(TARGET_FLAG ~ HOME_VAL + PARENT1 +  SEX + EDUCATION + CAR_USE  +REVOKED,  data = dat, family = "binomial")

summary(model5)

plot(model5)

## Model 6


model6 <- glm(TARGET_FLAG ~ HOME_VAL + PARENT1 +  SEX + EDUCATION + CAR_USE  +REVOKED + log10(INCOME + 1) + JOB + CLM_FREQ,  data = dat, family = "binomial")

summary(model6)

plot(model6)



```

## Select Model

We going to select model number 6 from logistic regression for which gives a better AIC result.in model number 6, we are using log() function on the income variable and selecting the most significant variables.

```{r}
test.data <- read.csv('insurance-evaluation-data.csv')

dat$pred<- predict(model6, dat, interval="response")

dat$target.pred<- ifelse(dat$pred >= 0.5, 1, 0)  

confusionMatrix(factor(dat$target.pred),factor(data$TARGET_FLAG))


roc.value <- roc(data$TARGET_FLAG, dat$pred, plot=TRUE, asp=NA,
                legacy.axes=TRUE, col="red")



# Testing Data

col <- c("HOME_VAL","OLDCLAIM","INCOME","BLUEBOOK")
test.data[col] <- sapply(test.data[col],as.numeric)

test.data$INCOME <- str_replace_all(test.data$INCOME, "[\\$,]", "")
test.data$HOME_VAL <- str_replace_all(test.data$HOME_VAL, "[\\$,]", "")
test.data$BLUEBOOK <-  str_replace_all(test.data$BLUEBOOK, "[\\$,]", "")
test.data$OLDCLAIM <- str_replace_all(test.data$OLDCLAIM, "[\\$,]", "")

col <- c("HOME_VAL","OLDCLAIM","INCOME","BLUEBOOK")
test.data[col] <- sapply(test.data[col],as.numeric)


test.data$MSTATUS <- ifelse(test.data$MSTATUS == "Yes", 1, 0)  
test.data$SEX <- ifelse(test.data$SEX == 'M', 1, 0)  
test.data$PARENT1 <- ifelse(test.data$PARENT1 == "Yes", 1, 0)  
test.data$CAR_USE <- ifelse(test.data$CAR_USE == "Private", 1, 0)  
test.data$RED_CAR <- ifelse(test.data$RED_CAR == "yes", 1, 0)  
test.data$REVOKED <- ifelse(test.data$REVOKED == "Yes", 1, 0)  
test.data$EDUCATION <- ifelse(test.data$EDUCATION == "<High School", 0, 1)  
test.data$URBANICITY <- ifelse(test.data$URBANICITY == "Highly Urban/ Urban", 1, 0)  
test.data$INCOME <- log10(as.numeric(test.data$INCOME)) + 1



test.data$pred <- predict(model6, newdata = test.data, interval="response")
test.data$target.pred<- ifelse(test.data$pred >= 0.5, 1, 0)  
head(test.data)





write.csv(test.data,"test_data_pred.csv")



```